### 2020-12-04 doc/thesis/chapters/introduction.tex
start table of contents

>>>>

Thesis Design Decisions: \\
\\
Main focus on system design. \\
\\
How to achieve the same result in 3 (4?) different levels of abstraction?

\begin{enumerate}
  \item GnuRadio (?)
  \item Matlab
  \item HLS\\
      Implementation targeting Xilinx' ZedBoard.\\
      Optionally: \\
      Intel as a comparison (synth only, no HW) - "How platform-independent is HLS?"
  \item VHDL
\end{enumerate}
\vspace{.5 cm}
Compare:
- Implementation effort (difficulty)
- Implementation time
- Usefulness on Target Systems (uC, SoC, RasPi, etc)
- others?
